My Cool Title

### 2019-05-06 paper.tex
Added more to abstract

\begin{abstract}
  The ActiVis project aims to deliver a system for a mobile device that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
  To do so, it uses new developments in object detection methods, mobile computing and action generation. 
  \keywords{Active vision, vision impairment, object detection}
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/environment.png}
  \caption{A picture of the experiment setup. }\label{fig:boxplot-time}
\end{figure}

>>>>

\begin{abstract}
  The ActiVis project aims to deliver a system for a mobile device that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
  To do so, it uses new developments in object detection methods, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present useful guidance directions.
  Our approach to action generation used a Markov Decision Process (MDP) to track the system's state and output the next best location to investigate to find a target object and has been shown to work in principle in~\cite{lock2019active}.
  This work expands upon that by adding an object detector and adapting the decision-making process accordingly, providing a complete object search and guidance pipeline.
  The improved ActiVis system was evaluated in a set of experiments and it outperformed the baseline, unguided case.
  \keywords{Active vision, vision impairment, object detection}
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/environment.png}
  \caption{A picture of the experiment setup. }\label{fig:experiment-env}
\end{figure}
